Plug-and-play dual-tree algorithm runtime analysis

### 2014-11-14 bounds-files/sec02-nearest-neighbor-search.tex
Refactor NNS section a bit.

\begin{thm}
Using cover trees, the standard cover tree pruning dual-tree traversal, and the
nearest neighbor search \texttt{BaseCase()} and \texttt{Score()} as given in
Algorithms \ref{alg:nn_base_case} and \ref{alg:nn_score}, respectively, and also
given a reference set $S_r$ with expansion constant $c_r$, a query set $S_q$,
and an inverse degree of bichromaticity $\nu$, the running time of the
algorithm is bounded by $O(c_r^4 c_{qr}^5 \nu N)$.
\label{thm:nns}
\end{thm}

\begin{proof}
The running time of \texttt{BaseCase()} and \texttt{Score()} are clearly $O(1)$.
Due to Theorem \ref{thm:ct-runtime}, we therefore know that the runtime of the
algorithm is bounded by $O(c_r^4 \nu |R^*| N)$.  Thus, the only thing that
remains is to bound the maximum size of the reference set, $|R^*|$.

@@

In the monochromatic case where $S_q = S_r$, the bound is $O(c^9 \nu N)$ because
$c = c_r = c_{qr}$.

>>>>

\begin{thm}
Using cover trees, the standard cover tree pruning dual-tree traversal, and the
nearest neighbor search \texttt{BaseCase()} and \texttt{Score()} as given in
Algorithms \ref{alg:nn_base_case} and \ref{alg:nn_score}, respectively, and also
given a reference set $S_r$ with expansion constant $c_r$, a query set $S_q$,
the running time of the algorithm is bounded by $O(c_r^4 c_{qr}^5 (N + \theta))$
with $\theta$ defined as in Theorem \ref{thm:ct-runtime}.
\label{thm:nns}
\end{thm}

\begin{proof}
The running time of \texttt{BaseCase()} and \texttt{Score()} are clearly $O(1)$.
Due to Theorem \ref{thm:ct-runtime}, we therefore know that the runtime of the
algorithm is bounded by $O(c_r^4 |R^*| (N + \theta))$.  Thus, the only thing
that remains is to bound the maximum size of the reference set, $|R^*|$.

@@

In the monochromatic case where $S_q = S_r$, the bound is $O(c^9 (N +
i_t(\mathscr{T}))$ because $c = c_r = c_{qr}$ and $\theta = i_t(\mathscr{T})$.
